---
title: "AE9110-1-22H_Biostatistics_coursework"
author: "Chidimma Echebiri"
date: "2022-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Data source
The  dataset used in this analyses was obtained from https://www.kaggle.com/datasets/konradb/norway-bicycle.
I will be using Bayesian theorem to note the impact of rain and temperature on the number of bike rides in Norway for a period of time.

I have the following hypotheses
1. The number of bikes on the road each day is influenced by the temperature alone
2. The number of bikes is influenced by how heavy the rain is
3. The number of bikes in influenced by a combination of the three factors

## Including Plots

You can also embed plots, for example:

```{r}

install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
```

```{r}
library(rstan)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(magrittr)
library(greta)
library(tensorflow)
library(bayesplot)
library(readr)
```

```{r}
rstan_options(auto_write = TRUE)
```

Loading the dataset
```{r}
bike_data <- readr::read_csv("./bikerides_day.csv")
summary(bike_data)
```

Some data wrangling
```{r}
rownames(bike_data) = bike_data$Date
```

Plot the distribution of the bike data
Volume = number of bikes in a day
Rain is the depth of rainfall per day
Temperature is the temperature that day
```{r}
plot(bike_data[-1])
```
Remove any missing data
```{r}
bike_data <- bike_data[complete.cases(bike_data),]

```
```{r}

#Date <- as.integer(factor(bike_data$Date))
```

Define and standardize model vars
```{r}
Number_bikes <- as_data(scale(bike_data$Volume))
Amount_rainfall <- as_data(scale(bike_data$Rain))
Temperature <- as_data(scale(bike_data$Temp))
```
````{r}

````